Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV

### 2018-01-15 fa_2017-08-29.tex
fa update

The ALICE Collaboration gratefully acknowledges the resources and support provided by all Grid centres and the Worldwide LHC Computing Grid (WLCG) collaboration.

@@

Ministry of Science \& Technology of China (MSTC), National Natural Science Foundation of China (NSFC) and Ministry of Education of China (MOEC) , China;

@@

Ministry of Science, Education and Sport and Croatian Science Foundation, Croatia;

@@

Ministry of Education, Youth and Sports of the Czech Republic, Czech Republic;

@@

The Danish Council for Independent Research | Natural Sciences, the Carlsberg Foundation and Danish National Research Foundation (DNRF), Denmark;

@@

Commissariat \`{a} l'Energie Atomique (CEA) and Institut National de Physique Nucl\'{e}aire et de Physique des Particules (IN2P3) and Centre National de la Recherche Scientifique (CNRS), France;

@@

The Research Council of Norway, Norway;

@@

Swedish Research Council (VR) and Knut \& Alice Wallenberg Foundation (KAW), Sweden;

@@

National Science Foundation of the United States of America (NSF) and United States Department of Energy, Office of Nuclear Physics (DOE NP), United States of America.

>>>>

The ALICE Collaboration gratefully acknowledges the resources and support provided by all grid centers and the Worldwide LHC Computing Grid (WLCG) collaboration.

@@

Ministry of Science and Technology of China (MSTC), National Natural Science Foundation of China (NSFC), and Ministry of Education of China (MOEC) , China;

@@

Ministry of Science, Education, and Sport and Croatian Science Foundation, Croatia;

@@

Ministry of Education, Youth, and Sports of the Czech Republic, Czech Republic;

@@

the Danish Council for Independent Research--Natural Sciences, the Carlsberg Foundation and Danish National Research Foundation (DNRF), Denmark;

@@

Commissariat \`{a} l'Energie Atomique (CEA), Institut National de Physique Nucl\'{e}aire et de Physique des Particules (IN2P3), and Centre National de la Recherche Scientifique (CNRS), France;

@@

the Research Council of Norway, Norway;

@@

Swedish Research Council (VR) and Knut and Alice Wallenberg Foundation (KAW), Sweden;

@@

and National Science Foundation of the United States of America (NSF) and United States Department of Energy, Office of Nuclear Physics (DOE NP), United States of America.
